Estimating Fixed Frame Galaxy Magnitudes in the SDSS$^1$

### 2003-03-30 docs/paper/paper.tex
tiny
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@183 75dff457-8751-0410-ab1a-cd701654ce6b

The SDSS (\citealt{york00a}) is producing imaging and spectroscopic
surveys over $\pi$ steradians in the Northern Galactic Cap. A
dedicated 2.5m telescope (Siegmund {\it et al.}, in preparation) at
Apache Point Observatory, Sunspot, New Mexico, images the sky in five
bands between 3000 and 10000 \AA\ ($u$, $g$, $r$, $i$, $z$;
\citealt{fukugita96a}) using a drift-scanning, mosaic CCD camera
(\citealt{gunn98a}), detecting objects to a flux limit of $r'\sim
22.5$. The ultimate goal is to spectroscopically observe Main Sample
galaxies 900,000 galaxies (down to $r_{\mathrm{lim}}\approx 17.77$;
\citealt{strauss02a}), 100,000 Luminous Red Galaxies (LRGs;
\citealt{eisenstein01a}), and 100,000 QSOs (\citealt{fan99a}; Newberg
{\it et al.}, in preparation).  This spectroscopic follow up uses two
digital spectrographs on the same telescope as the imaging
camera. Many of the details of the galaxy survey are described in a
description of the galaxy target selection paper
(\citealt{strauss02a}). Other aspects of the survey are described in
the Early Data Release (EDR; \citealt{stoughton02a}).

>>>>

The SDSS (\citealt{york00a}) is producing imaging and spectroscopic
surveys over $\pi$ steradians in the Northern Galactic Cap. A
dedicated 2.5m telescope (Siegmund {\it et al.}, in preparation) at
Apache Point Observatory, Sunspot, New Mexico, images the sky in five
bands between 3000 and 10000 \AA\ ($u$, $g$, $r$, $i$, $z$;
\citealt{fukugita96a}) using a drift-scanning, mosaic CCD camera
(\citealt{gunn98a}), detecting objects to a flux limit of $r'\sim
22.5$. The ultimate goal is to spectroscopically observe 900,000 Main
Sample galaxies (down to $r_{\mathrm{lim}}\approx 17.77$;
\citealt{strauss02a}), 100,000 Luminous Red Galaxies (LRGs;
\citealt{eisenstein01a}), and 100,000 QSOs (\citealt{fan99a};
\citealt{richards02a}.  This spectroscopic follow up uses two digital
spectrographs on the same telescope as the imaging camera. Many of the
details of the galaxy survey are described in a description of the
galaxy target selection paper (\citealt{strauss02a}). Other aspects of
the survey are described in the Early Data Release (EDR;
\citealt{stoughton02a}).
